Model behavior analysis

### 2016-10-15 Rmd/analyze.Rmd
move amp. & PI curve to supplement

### Light amplification & self-shading
```{r lightamp, fig.width=5, fig.height=5, eval=T, include=T}
# Import data from Marcelino et al. 2013
md <- read.csv("data/marcelino2013_fig2a.csv")
md$S.R <- md$density * cm2.m2 / CmolR.m2 * CmolS.cellS  # Convert units of symbiont density to CmolS/CmolR
md$A <- md$E + 1  # Convert "E"=excess light metric of Marcelino to "A"=amplification factor
# Plot data
plot(md$A ~ md$S.R, pch=c(21,23,22)[factor(md$spp)], bg=c("white", "black", "gray")[factor(md$spp)], 
     ylab="internal/external light", ylim=c(1,3.2),
     xlab="Symbiont density (CmolS/CmolR)",
     main="Light Amplification")
legend("topright", legend=levels(md$spp), pch=c(21,23,22), pt.bg=c("white", "black", "gray"), inset=0.02)
# Fit exponential decay model and plot fitted values
mod <- nls(A ~ x + y * exp(z * S.R), data=md, start=list(x=1, y=2, z=-3))
fit <- predict(mod, list(S.R=seq(0, 0.5, 0.01)))
lines(fit ~ seq(0, 0.5, 0.01))
# Get parameters of fit
formula(mod); coef(mod)
```

### PI curve
```{r run1_PI, cache=T, fig.height=3}
sym_PI(pars=defpars)
```

@@

# Run to steady state and plot results
ssdat <- run_steady_states(pars=replace(defpars, c("initS", "kCO2"), c(1, 10)), at=at, food=5e-6, runtime=T)
plot_steady_states(ssdat)
```
With default parameters, steady state values of specific growth are higher than usually observed in corals (skeletal growth), but patterns across environments are consistent with literature.

@@

# Initialize environment
env <- init_env(time=time, L=c(20,20,2), N=c(1e-7,4e-6,2), X=c(0,0,0))

@@

# Run simulation
run <- run_coral(time=time, env=env, pars=replace(defpars, c("initS", "kCO2"), c(0.25, 10)))#
plot_run(run)
```

@@

# Initialize environment
env <- init_env(time=time, L=c(5,30,2), N=c(1e-7,1e-7,0), X=c(5e-6,5e-6,0))

@@

>>>>

@@

# Run to steady state and plot results
ssdat <- run_steady_states(pars=defpars, at=at, food=5e-6, runtime=T)
plot_steady_states(ssdat)
```
With default parameters, steady state values of specific growth are higher than usually observed in corals (skeletal growth), but patterns across environments are consistent with literature.

@@

# Initialize environment
env <- init_env(time=time, L=c(20,20,2), N=c(1e-8,4e-6,2), X=c(0,0,0))

@@

# Run simulation
run <- run_coral(time=time, env=env, pars=defpars)
plot_run(run)
```

@@

# Initialize environment
env <- init_env(time=time, L=c(5,30,2), N=c(1e-7,1e-7,0), X=c(0,0,0))

@@

# Run simulation
run <- run_coral(time=time, env=env, pars=defpars)#
plot_run(run)
```

### Dynamic behavior: food
```{r varyX, eval=T, include=T, fig.width=5}
# Set run time vector
time <- seq(1, 365, 0.5)  # if single model run, use time input

# Initialize environment
env <- init_env(time=time, L=c(20,20,2), N=c(1e-8,1e-8,0), X=c(0,10e-6,1))

# Run simulation
run <- run_coral(time=time, env=env, pars=replace(defpars, c("initS", "kCO2", "nNH"), c(0.2, 10, 0.19)))#
plot_run(run)
```
